An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex

\begin{document} 
\twocolumn[\icmltitle{Handwriting Recognition}
\icmlauthor{Jarre Knockaert}{Jarre.Knockaert@UGent.be}
\icmlauthor{Ruben Dedecker}{Ruben.Dedecker@UGent.be}

\vskip 0.3in
]
% Notes:
% - Add https://tel.archives-ouvertes.fr/tel-01249405/document reference, (see abstract) 
% in order to compare results. 
% - Disciss possible flaws. (Use images from IAM in order to do so)
% - Update outdated parts, like neural net of splitpoint evaluation
%  Reference datasets, Chars74K, IAM, Google n-grams
%  redo the preprocessing experiment and explain why some techniques increase the accuracy more than others. 
\begin{abstract} 
The aim of this paper is to present a system for off-line handwriting recognition. 
We discuss how to segment texts with contouring. Next we present our method of segmentating words into characters. 
Then we describe how to recognise characters with a deep neural network approach. 
Finally we present some postprocessing techniques to correct mispredicted text. 
\end{abstract}

@@

First we explain how to recognise characters in Section \ref{sec:charrec}. This explanation involves the used dataset, preprocessing techniques and the deep neural network for classifying characters. 
In Section \ref{sec:segtext} we describe how to segment a text into words using a contouring algorithm with consequent postprocessing to remove unwanted noise. 
After this we present our approach to seperating the characters from words in \ref{seg:segword}. We use vertical projections combined with postprocessing techniques including a neural network for segmentation point evaluation.
Postprocessing steps are presented in Section \ref{seg:postproc}, we try to correct word recognition errors using an English dictionary and language models, n-gram models in particular.
We conclude this paper with some experimental results, the problems we encountered combined with possible improvements.

@@

\subsection{Data}
\label{sec:data}
Before exposing the neural network to new characters, it needs to be familiar with many training samples to be able to classify any new character correctly. 
This is a why a good dataset is very important. A dataset should have many examples, much variation, and an even balance between classes. A dataset with these properties 
allow the neural network to train effectively and recognise any new character given to the network.

@@

\begin{figure}
\begin{subfigure}{.23\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/bad_char1}
  \caption{Picture of a 'z' which resembles a 7.}
\end{subfigure}
\begin{subfigure}{.23\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/bad_char2}
  \caption{Picture of a 'z' which resembles a 3.}
\end{subfigure}
\caption{Examples of written 'z' characters, which are hard to recognise.}
\label{fig:char}
\end{figure}

@@

\paragraph{Adding noise to data}
We add a variant of each image which includes noise troughout the image with the purpose of reducing overfitting of the neural network \cite{DataNoise}. This noise is taken from the Gaussian distribution with a mean of 0 and standard deviation of 0.004. The noise is summed with the original image of which the pixels are normalized between $[-1, 1]$.
\paragraph{Translations of data}
The dataset is also extended with variations in padding of characters in images. For this purpose we multiply every coordinate of the original image with the following transformation matrix: 
\begin{equation}
        \begin{bmatrix}
                1 & 0 & t_x \\
                0 & 1 & t_y
        \end{bmatrix}
\end{equation}
where $t_x$ is the horizontal shift and $t_y$ is the vertical shift. The values for chosen for $t_x$ are -8, 0 and 8, the values chosen for $t_y$ are -4, 0 and 4. All combinations are used except $t_x=0$ and $t_y=0$. The translation only occurs if it does not displace the character outside of the image.
\paragraph{Rotations of data}
Rotations of the image are added to the dataset to make the network more robust to handwritings with different orientations. This matrix is equal to:
\begin{equation}
       \begin{bmatrix}
               \alpha & \beta & (1-\alpha)*center.x - \beta*center.y \\
               -\beta & \alpha & \beta*center.x + (1-\alpha)*center.y
       \end{bmatrix}
\end{equation}
where $\alpha = cos(angle)$ and $\beta = sin(angle)$. $center$ is the coordinate in our image around which is rotated and the angle describes the amount of degrees to rotate in the clockwise direction. We use -30 and 30 as angle.
\paragraph{Scaling of data}
With the purpose of making the network more robust to different sizes of handwriting, we add different scalings of the data. We scale in both the horizontal and vertical direction. The following transformation matrix allows us to scale the input image: 
\begin{equation}
       \begin{bmatrix}
               s_x & 0 & 0  \\
               0 & s_y & 0
       \end{bmatrix}
\end{equation}
where $s_x$ is the horizontal scaling factor and $s_y$ is the vertical scaling factor. 
We use combinations of values in $[0.75, 1, 1.25, 1.5]$ for $s_x$ and $s_y$ depending on the original size of the character.
\paragraph{Shearing of data}
In order to deal with different kinds of slants we add sheared versions of the image to the dataset. 
Shearing displaces each point in a fixed direction, by an amount proportional to its signed distance from a line that is parallel to that direction \cite{Shear}. We used the following shear mapping to achieve this: 
\begin{equation}
        \begin{bmatrix}
                1 & s & 0 \\
                0 & 1 & 0
        \end{bmatrix}
\end{equation}
\paragraph{Erosion of data}
The erosion operation of images adds thinner versions of characters to the dataset. Erosion uses a kernel to convolute an image. 
The image is scanned using the kernel. The maximum pixel value of the overlapping part between the image and the kernel is computed. This pixel value of the anchor point of the kernel is replaced with the maximum pixel value. 
This causes bright regions to get thinner and dark regions to get bigger in the image.  
All of the previously discussed preprocessing techniques are also applied to the eroded image. The final dataset contains translated, orientated, sheared, scaled and noisy versions of both the original image and the eroded image. A visualitation of the augmentation of an augmented picture can be seen in Figure \ref{fig:augmented}.

\begin{figure}
\begin{subfigure}{0.11\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/original}
  \caption{Original image}
\end{subfigure}
\begin{subfigure}{0.11\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/noisy}
  \caption{Noisy image}
\end{subfigure}
\begin{subfigure}{0.11\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/translated}
  \caption{Translated image}
\end{subfigure}
\begin{subfigure}{0.11\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/rotated}
  \caption{Rotated image}
\end{subfigure}
\begin{subfigure}{0.11\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/scaled}
  \caption{Scaled image}
\end{subfigure}
\begin{subfigure}{0.11\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/sheared}
  \caption{Sheared image}
\end{subfigure}
\begin{subfigure}{0.11\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/eroded}
  \caption{Eroded image}
\end{subfigure}
\caption{All of the augmentations applied to one image.}
\label{fig:augmented}
\end{figure}
\subsection{Deep neural network}
\label{sec:dnn}
% TODO: make a drawing, see http://www.ais.uni-bonn.de/deep_learning/images/Convolutional_NN.jpg
Humans have millions of connected neurons in the visual cortices which are capable of image processing.
We can recognise most characters without any thought because of this complex neural network inside our brain. 
For computers, character recognition is a more difficult task. We could try to write rule-based systems and define how every character should look. This solution is not flexible at all and is very hard to define.
We use a neural network, inspired by how the brain processes images. These deep neural networks contain several layers of connected perceptrons, where each connection is defined by weight and each perceptron is defined by a bias. 
The perceptrons take an input and calculate an output using an activation function. This allows perceptrons to make decisions.  
Normalized images can be fed to the neural network, which then propagate through several layers and eventually produce as output the probability that the input image has a certain class, one of the possible characters. 
Now follows a detailed overview of our deep neural network. A detailed explanation on how deep neural networks function is explained by \cite{nnbook}.

@@

\section{Segmentation of text into words}
\ref{sec:segtext}

@@

We take a slightly different approach and consider a deep neural network to tackle this problem. This allows us to use convolutational layers in order to extract features, instead of manually creating features (features which show the density in this case). 
We use one convolutional layer and three fully connected layers in our neural network. This neural network takes the actual image of the segmentation point as input (a pixel matrix of the pixels surrounding the segmentation point) and returns a one-hot encoded vector indicating if the segmentation is correct or incorrect. 
This method allowed us to achieve a higher accuracy than an implementation of the method described by \cite{evalsplitpointsnn}.
Segmentation points can now be filtered if the neural network decides a segmentation point is incorrect.

@@

where $w_i$ is the word of which we want to calculate the probability and $count(w_i,...w_{i+n})$ indicates the amount of occurences of $w_i,...,w_{i+n}$. That amount is the same as counting the amount of n-grams with that sequence of words. An n-gram is a sequence of n words from a given sequence of text, denoted as $w_i,...,w_{i+n}$. \cite{ngrams} % TODO google citation% 

@@

\label{sec:expres}
We tested a lot of different configurations for the deep neural network in order to find a good functioning neural network given the low amounts of data. A problem which arrised when trying to test many different configurations was the long time it takes to train a neural network. 
In order to limit the time these experiments run we added some small constraints. We only run every experiment 200 epochs, running these experiments longer might result in different conclusions. 
Next it is important to note that a lot of stochastic behaviour is part of these neural networks because of the dropout layers. When running the neural network twice with the same configuration, it could have completely different results. This is why we run every configuration four times. Only the result with the highest accuracy is considered. This way we can avoid outliers. 
Another note is that some experiments might not use the finalized setup of our neural network. These experiments do use the same setup to compare different configurations. 
\subsubsection{Experiments}
\paragraph{Preprocessing techniques} 
Figure \ref{fig:preprocess} shows that preprocessing techniques have great influence on the performance of the neural network. We can see that the accuracy is much higher when using all of the preprocessing techniques.  
We achieve 72\% accuracy with all of the preprocessing techniques versus 35\% without any preprocessing techniques, which is a huge difference. 
We can also see the individual impact of preprocessing in the figure. Adding shearing (64\%) to handle different amounts of slant, adding noise (58\%) to cope to make the recognition more robust and adding scaling (59\%) to handle different handwriting sizes was the most effective to increase performance. Adding rotations (40\%) and translations (50\%) was less effective (but still effective). Adding these preprocessing techniques increased the amount of data greatly from 3410 examples to 37000 examples. This improves the performance but also increases the training time of our network significantly. One remarkable result is that the training time of preprocessing with all techniques enabled, takes shorter time than some other results. When we look at the average however, the training time is the highest for this case. 
\paragraph{Learning rate}
Figure \ref{fig:learningrate} shows the impact of learning rate on the training of our neural network. 
For this experiment we do have to note that we are using the Adam optimizer to train our neural network which computes individual learning rates for every parameter every training step. The learning rate which we pass is the initial learning rate. Choosing a high learning rate $10^{-3}$ allows the neural network to converge to a high accuracy (76 \%) very fast, but once reached the accuracy fails to grow any more.
This in contrast to higher learning rates which reach a good accuracy more slowly but find a more optimal solution. Learning rate $10^{-4}$ reaches an accuracy of 68\% after 200 iterations but is still growing. Learning rate $10^{-5}$ only reaches an accuracy of 5\% after 200 iterations but should find a better solution eventually than the other two configurations. 
\paragraph{Batch size}
n Figure \ref{fig:batchsize} we can see the impact of choosing different batch sizes which are fed to the neural network. In order to increase the speed at which the neural network is trained, we feed batches of input images to the neural network instead of one image at a time. 
Weight adjustment only occurs after feeding a complete batch to the network. In the figure we can see bigger batch sizes increase the execution speed. However these differences are quite small. The configuration with batch size executes 200 iterations in one minute less than a configuration with batch size 128. These batch sizes also have an effect on our performance. When using small batch sizes backpropagation happens more frequently, which implies our weights will be more finetuned. The configuration with batch size 128 obtains an accuracy of 10\% higher than batch size 1024.
\paragraph{Weight decay}
In order to regulize the neural network we add weight decay to the network loss function in order to penalize big weights. The impact of different decays can be seen in Figure \ref{fig:decay}. A high decay functions best (71\% accuracy) because we have a small amount of training examples. Without decay we only reach an accuracy of 65\%. 
\paragraph{Dropout}
% Maybe redo this experiment? It's not clear at all at this time whether dropout has an actual effect on the accuracy. I believe it helps find a better global solution, but often the accuracy will be lower as we're only using half of the weights. Further research is required. 
\centering
    \includegraphics[width=\linewidth]{../Graphs/preprocess.png}
    \caption{Impact of various preprocessing techniques.}
    \label{fig:preprocess}
    \centering
    \includegraphics[width=\linewidth]{../Graphs/learningrate.png}
    \caption{Impact of different learning rates.}
    \label{fig:learningrate}
    \centering
    \includegraphics[width=\linewidth]{../Graphs/batchsize.png}
    \caption{Impact of different batch sizes.}
    \label{fig:batchsize}
    \centering
    \includegraphics[width=\linewidth]{../Graphs/decay.png}
    \caption{Impact of weight decay regularisation.}
    \label{fig:decay}
\subsubsection{Final results}
% Add graph with several runs of the final network. Discuss which parameters we took. 
% Maybe some more visualisation of mispredicted characters? Oh this isn't part of char recognition...
% TODO TODO

@@

\section{Future research}

\bibliography{paper}
\bibliographystyle{icml2016}

>>>>

\begin{document} 
\twocolumn[\icmltitle{An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks}
\icmlauthor{Jarre Knockaert}{Jarre.Knockaert@UGent.be}
\icmlauthor{Ruben Dedecker}{Ruben.Dedecker@UGent.be}

\vskip 0.3in
]
% Notes:
%  redo the preprocessing experiment and explain why some techniques increase the accuracy more than others. 
\begin{abstract} 
The aim of this paper is to present a complete system for off-line handwriting recognition. 
We discuss how to segment texts with contouring. Next we present our method of segmentating words into characters. 
Then we describe how to recognise characters with a deep neural network approach. 
Finally we present some postprocessing techniques to correct mispredicted text. 
\end{abstract}

@@

First we explain how to recognise characters in Section \ref{sec:charrec}. This explanation involves the used dataset, preprocessing techniques and the deep neural network for classifying characters. 
In Section \ref{sec:segtext} we describe how to segment a text into words using a contouring algorithm with consequent postprocessing to remove unwanted noise. 
After this we present our approach to seperating the characters from words in \ref{seg:segword}. We use vertical projections combined with postprocessing techniques including a neural network for segmentation point evaluation.
Postprocessing steps are presented in Section \ref{seg:postproc}, we try to correct word recognition errors using an English dictionary and language models, n-gram models in particular.
We conclude this paper with some experimental results, the problems we encountered combined with possible improvements. A complete flow of the recognition of an image is shown in Figure \ref{fig:flow}.

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{images/flow_hor}
  \caption{All of the steps in our system to convert an image with handwritten text to digitalized text.}
  \label{fig:flow}
\end{figure*}

@@

\subsection{Dataset}
\label{sec:data}
Before exposing the neural network to new characters, it needs to be familiar with many training samples to be able to classify any new character correctly. 
This is a why a good dataset is very important. A dataset should have many examples, much variation, and an even balance between classes. A dataset with these properties 
allow the neural network to train effectively and recognise any new character given to the network.

@@

\begin{figure}
\begin{subfigure}{.23\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/bad_char1}
\end{subfigure}
\begin{subfigure}{.23\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/bad_char2}
\end{subfigure}
\caption{Examples of written 'z' characters, which are hard to recognise or ambiguous.}
\label{fig:char}
\end{figure}

@@

\paragraph{Translations of data}
The dataset is also extended with variations in padding of characters in images. For this purpose we multiply every coordinate of the original image with the following transformation matrix: 
\begin{equation}
        \begin{bmatrix}
                1 & 0 & t_x \\
                0 & 1 & t_y
        \end{bmatrix}
\end{equation}
where $t_x$ is the horizontal shift and $t_y$ is the vertical shift. The values for chosen for $t_x$ are -8, 0 and 8, the values chosen for $t_y$ are -4, 0 and 4. All combinations are used except $t_x=0$ and $t_y=0$. The translation only occurs if it does not displace the character outside of the image.
\paragraph{Rotations of data}
Rotations of the image are added to the dataset to make the network more robust to handwritings with different orientations. This matrix is equal to:
\begin{equation}
       \begin{bmatrix}
               \alpha & \beta & (1-\alpha)*center.x - \beta*center.y \\
               -\beta & \alpha & \beta*center.x + (1-\alpha)*center.y
       \end{bmatrix}
\end{equation}
where $\alpha = cos(angle)$ and $\beta = sin(angle)$. $center$ is the coordinate in our image around which is rotated and the angle describes the amount of degrees to rotate in the clockwise direction. We use -30 and 30 as angle.
\paragraph{Scaling of data}
With the purpose of making the network more robust to different sizes of handwriting, we add different scalings of the data. We scale in both the horizontal and vertical direction. The following transformation matrix allows us to scale the input image: 
\begin{equation}
       \begin{bmatrix}
               s_x & 0 & 0  \\
               0 & s_y & 0
       \end{bmatrix}
\end{equation}
where $s_x$ is the horizontal scaling factor and $s_y$ is the vertical scaling factor. 
We use combinations of values in $[0.75, 1, 1.25, 1.5]$ for $s_x$ and $s_y$ depending on the original size of the character.
\paragraph{Shearing of data}
In order to deal with different kinds of slants we add sheared versions of the image to the dataset. 
Shearing displaces each point in a fixed direction, by an amount proportional to its signed distance from a line that is parallel to that direction \cite{Shear}. We used the following shear mapping to achieve this: 
\begin{equation}
        \begin{bmatrix}
                1 & s & 0 \\
                0 & 1 & 0
        \end{bmatrix}
\end{equation}
\paragraph{Erosion of data}
The erosion operation of images adds thinner versions of characters to the dataset. Erosion uses a kernel to convolute an image. 
The image is scanned using the kernel. The maximum pixel value of the overlapping part between the image and the kernel is computed. This pixel value of the anchor point of the kernel is replaced with the maximum pixel value. 
This causes bright regions to get thinner and dark regions to get bigger in the image.  
All of the previously discussed preprocessing techniques are also applied to the eroded image. The final dataset contains translated, orientated, sheared and scaled versions of both the original image and the eroded image. A visualitation of the augmentation of an augmented picture can be seen in Figure \ref{fig:augmented}.

\begin{figure}
\begin{subfigure}{0.15\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/original}
  \caption{Original}
\end{subfigure}
\begin{subfigure}{0.15\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/translated}
  \caption{Translated}
\end{subfigure}
\begin{subfigure}{0.15\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/rotated}
  \caption{Rotated}
\end{subfigure}
\begin{subfigure}{0.15\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/scaled}
  \caption{Scaled}
\end{subfigure}
\begin{subfigure}{0.15\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/sheared}
  \caption{Sheared}
\end{subfigure}
\begin{subfigure}{0.15\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/eroded}
  \caption{Eroded}
\end{subfigure}
\caption{An image transformed by the discussed augmentation techniques.}
\label{fig:augmented}
\end{figure}
\subsection{Deep neural network}
\label{sec:dnn}
% TODO: make a drawing, see http://www.ais.uni-bonn.de/deep_learning/images/Convolutional_NN.jpg
Humans have millions of connected neurons in the visual cortices which are capable of image processing.
We can recognise most characters without any thought because of this complex neural network inside our brain. 
For computers, character recognition is a more difficult task. We could try to write rule-based systems and define how every character should look. This solution is not flexible at all and is very hard to define.
We use a neural network, inspired by how the brain processes images. These deep neural networks contain several layers of connected perceptrons, where each connection is defined by weight and each perceptron is defined by a bias. 
The perceptrons take an input and calculate an output using an activation function. This allows perceptrons to make decisions.  
Normalized images can be fed to the neural network, which then propagate through several layers and eventually produce as output the probability that the input image has a certain class, one of the possible characters. 
Now follows a detailed overview of our deep neural network. This overview is visualized in Figure \ref{fig:dnn}. A detailed explanation on how deep neural networks function is explained by \cite{nnbook}.

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{images/dnn}
  \caption{Visualization of the deep neural network for character recognition. The first row shows the shape a layer. The second row shows the visualization of that layer, the third row shows information about the layer. 'C' indicates a convolutional layer, 'MP' a max-pooling layer and 'FC' a fully-connected layer.}
  \label{fig:dnn}
\end{figure*}

@@

The Adam optimizer minimizes the error calculated by the cross-entropy cost function adjusted with a weight decay factor. Weight decay regulizes the neural network by penalizing big weights and promoting smaller weights. Neural networks with this constraint tend to overfit less because small weights are less sensible to small changes of the input. \cite{presham}
\section{Segmentation of text into words}
\ref{sec:segtext}

@@

We take a slightly different approach and consider a deep neural network to tackle this problem. This allows us to use the power of convolutational layers to extract features, instead of manually creating features (features which show the density in this case). 
We use one convolutional layer and three fully connected layers in our neural network. This neural network takes the actual image of the segmentation point as input (a pixel matrix of the pixels surrounding the splitting point) and returns a one-hot encoded vector indicating if the splitting is correct or incorrect. 
This method allowed us to achieve a higher accuracy than an implementation of the method described by \cite{evalsplitpointsnn}.
Segmentation points can now be filtered if the neural network decides a segmentation point is incorrect.

@@

where $w_i$ is the word of which we want to calculate the probability and $count(w_i,...w_{i+n})$ indicates the amount of occurences of $w_i,...,w_{i+n}$. That amount is the same as counting the amount of n-grams with that sequence of words. An n-gram is a sequence of n words from a given sequence of text, denoted as $w_i,...,w_{i+n}$. \cite{ngrams} 

@@

The deep neural network can recognise characters with an accuracy of 91 \%. This neural network was trained for 1000 iterations which took 8650 seconds. We used a learning rate of $10^{-4}$, 256 as batch size, dropout layers with a keep probability of 0.5 and $10^{-3}$ as weight decay. Experimental findings led us to these values.

Comparisons are hard to find as few papers discuss off-line handwritten character recognition.
One paper we found, \cite{charrec}, achieves an accuracy of 98.5 \%, they classify 38 classes (10 digits, 26 letters, 2 special symbols) and manually extract features for the neural network instead of using convolutional layers.

\subsection{Influence of data augmentation on character recognition}

We're using the following setup for this experiment. Every experiment uses the original data in addition with the augmented data using one particular preprocessing technique. The base case without preprocessing techniques, just uses a copy of every image as augmented dataset.

In order to limit the time these experiments run we added some small constraints. We only run every experiment 200 epochs, running these experiments longer might result in different conclusions. 
Next it is important to note that a lot of stochastic behaviour is part of these neural networks because of the dropout layers. We run every configuration four times. Only the result with the highest accuracy is considered to avoid outliers. 
The accuracy decreases when using preprocessing techniques because the variety of our dataset increases but these techniques allow a more robust neural network which can recognise characters which includes images with more variation.

Figure \ref{fig:preprocess} shows that augmentation techniques have great influence on the performance of the neural network. However these results might seem counterintuitive. 
All preprocessing techniques have a lower accuracy than the base case which does not use preprocessing techniques. The amount of decrease in accuracy can be explained by how much the original image and augmented image differ. The configuration with erosion achieves the second highest accuracy, as these images resemble the original images most, the shape, position and rotation of the image remains, the density of regions in the image has only changed. A dataset with scaled images instead has much lower accuracy. As the image is completely different, the pixels are in other positions and the original shape has changed, the shape has a smaller or bigger surface depending on the kind of scaling.

In the final dataset we use augment every image once or more with every technique which causes the dataset to significantly increase in size. The accuracy of the configuration with augmented images is only higher because of the increase in data which allows more weight adjustment. Figure \ref{fig:allprep} shows the comparison of using no preprocessing techniques and all preprocessing techniques once or more.

\begin{figure}
\centering
    \includegraphics[width=\linewidth]{../Graphs/preprocess.png}
    \caption{Impact of various preprocessing techniques.}
    \label{fig:preprocess}
\end{figure}

@@

\section{Future research}
State-of-the-art systems currently use segmentation-free approaches, this involves handwriting recognition without explicitly splitting words into characters. These methods are mostly based on hidden Markov models and neural networks. This concept is explained and applied by \cite{presham}.
\section{Acknowledgements}
We thank Sarah Vluymans for her comments on this paper.
\bibliography{paper}
\bibliographystyle{icml2016}
